Lab 2 Final Report: COVID-19 Case Rate vs Population Demographics and Mask Policy

### 2020-12-10 Jackson_Liu_Temlock_Zhang_Lab2_Final_Report.Rmd
Added titles to the LCE plots

df<- df%>% 
  mutate(
    model1_preds = predict(model1), 
    model1_resids = resid(model1)
  ) 
df %>% 
  ggplot(aes(model1_preds, model1_resids)) + 
  geom_point() + 
  stat_smooth()
```

@@

```{r, warning=FALSE, message=FALSE}
df<- df%>% 
  mutate(
    model2_preds = predict(model2), 
    model2_resids = resid(model2)
  ) 
df %>% 
  ggplot(aes(model2_preds, model2_resids)) + 
  geom_point() + 
  stat_smooth()
```

@@

df<- df%>% 
  mutate(
    model3_preds = predict(model3), 
    model3_resids = resid(model3)
  ) 
df %>% 
  ggplot(aes(model3_preds, model3_resids)) + 
  geom_point() + 
  stat_smooth()
```

>>>>

df<- df%>% 
  mutate(
    model1_preds = predict(model1), 
    model1_resids = resid(model1)
  ) 
df %>% 
  ggplot(aes(model1_preds, model1_resids)) + 
  geom_point() + 
  stat_smooth() +
  labs(
    title = 'Model 1 Predicted vs Residuals', 
    x = 'Residuals', 
    y = 'Predicted'
  )
```

@@

```{r, warning=FALSE, message=FALSE}
df<- df%>% 
  mutate(
    model2_preds = predict(model2), 
    model2_resids = resid(model2)
  ) 
df %>% 
  ggplot(aes(model2_preds, model2_resids)) + 
  geom_point() + 
  stat_smooth() +
  labs(
    title = 'Model 2 Predicted vs Residuals', 
    x = 'Residuals', 
    y = 'Predicted'
  )
```

@@

df<- df%>% 
  mutate(
    model3_preds = predict(model3), 
    model3_resids = resid(model3)
  ) 
df %>% 
  ggplot(aes(model3_preds, model3_resids)) + 
  geom_point() + 
  stat_smooth() + 
  labs(
    title = 'Model 3 Predicted vs Residuals', 
    x = 'Residuals', 
    y = 'Predicted'
  )
```
